---
title: "LN Trm scRNA-seq Analysis"
author: "Austin Schultz (GitHub: aschultz37)"
date: "February 3, 2023"
output: html_document
---

# Initialization Code
Run once per R session.
```{r initialize, echo=TRUE, message=FALSE, results='hide'}
library(SCENIC)

setwd("/gpfs/home/acs9950/singlecell/2022-12-29/SCENIC/")

# Run commented code only if RDS does not exist.
# scenicOptions <- initializeScenic(org="mgi",
#                                   dbDir="resources/cisTarget_databases")
# motifAnnotations_mgi <- motifAnnotations
# scenicOptions <- initializeScenic(org="mgi",
#                                   dbDir="resources/cisTarget_databases")
# saveRDS(scenicOptions, file="resources/scenicOptions.Rds")

scenicOptions <- readRDS("resources/scenicOptions.Rds")
```

Create loom based on Seurat object. Only run if loom does not already exist.
```{r load_seurat}
# library(dplyr)
# library(Seurat)
# library(loomR)
# library(SeuratDisk)
# seurat_obj <- readRDS("../LN/output/2022-12-29_LN_sub1_rmbc_figs.rds")
# lnloom <- as.loom(seurat_obj)
```

Load data from loom file.
```{r load_loom, echo=TRUE, message=FALSE, results='hide'}
library(SCopeLoomR)

loom <- open_loom("2022-12-29.loom", mode="r+")
exprMat <- get_dgem(loom)
cellInfo <- get_cell_annotation(loom)
close_loom(loom)
```

Co-expression network. This block will give an error because whoever wrote the
package did not care to update dependencies in their code.
```{r coexpression}
genesKept <- geneFiltering(exprMat, scenicOptions)
exprMat_filtered <- exprMat[genesKept, ]
runCorrelation(exprMat_filtered, scenicOptions)
exprMat_filtered_log <- log2(exprMat_filtered+1) 
runGenie3(exprMat_filtered_log, scenicOptions) # causes error, run next block
```

Have to re-run this part because of the above error.
```{r re_coexpression}
motifAnnotations_mgi <- motifAnnotations
runGenie3(exprMat_filtered_log, scenicOptions)
```

Build and score the GRN.
```{r grn}
exprMat_log <- log2(exprMat+1)
scenicOptions@settings$dbs <- scenicOptions@settings$dbs["10kb"] # Toy run settings
scenicOptions <- runSCENIC_1_coexNetwork2modules(scenicOptions)
scenicOptions <- runSCENIC_2_createRegulons(scenicOptions, coexMethod=c("top5perTarget")) # Toy run settings
scenicOptions <- runSCENIC_3_scoreCells(scenicOptions, exprMat_log)
```

Optional: binarize activity.
```{r binarize}
scenicOptions <- runSCENIC_4_aucell_binarize(scenicOptions)
tsneAUC(scenicOptions, aucType="AUC") # choose settings
```

Export as loom.
```{r export_loom}
export2loom(scenicOptions, exprMat)
```

Save current status and settings.
```{r save_status}
saveRDS(scenicOptions, file="int/scenicOptions.Rds") 
```



